Generalized Plackett-Luce Likelihoods

### 2024-05-08 inst/paper.tex
issue #153, bullet point 2
issue #153, bullet point 3 (affiliation)

\author{Robin K. S. Hankin\\Auckland University of Technology}
\title{Generalized Plackett-Luce Likelihoods}
\Plainauthor{Robin K. S. Hankin} %% comma-separated
\Plaintitle{Generalized Plackett-Luce Likelihoods}

@@

%% The address of (at least) one author should be given
%% in the following format:
\Address{
  Robin K. S. Hankin\\
  School of Engineering and Mathematical Sciences\\
  Auckland University of Technology\\
  Wellesley Street\\
  Auckland, New Zealand\\
  E-mail: \email{hankin.robin@gmail.com}\\
  URL: \url{https://academics.aut.ac.nz/robin.hankin}
}

>>>>

\author{Robin K. S. Hankin~\orcidlink{0000-0001-5982-0415}\\
  The University of Stirling}
\title{Generalized Plackett-Luce Likelihoods}
\Plainauthor{Robin K. S. Hankin} %% comma-separated
\Plaintitle{Generalized Plackett-Luce Likelihoods}

@@

%% The address of (at least) one author should be given
%% in the following format:
\Address{
  Robin K. S. Hankin\\
  The University of Stirling\\
  Scotland\\
  E-mail: \email{hankin.robin@gmail.com}\\
  URL: \url{https://www.stir.ac.uk/people/1966824}
}
